\ecvsection{Conferences}%

\ecvitem[10pt]{}{12$^{th}$ International Conference on Zinc and Zinc Alloy Coated Steel. Virtual Conference, 21st to 23rd June 2021. Oral presentation. W. Dal'Maz Silva, H. Saint-Raymond, C. Dulcy. An integrated methodology for the root cause analysis of mechanical and metallurgical defects in hot-dip galvanized coatings.}

\ecvitem[10pt]{}{43$^e$ Congrès du Traitement Thermique et de l'Ingénierie des Surfaces. Nancy, France, 8th and 9th June 2016.  Oral presentation. W. Dal'Maz Silva, J. Dulcy, J. Ghanbaja, G. Michel, P. Lamesle, T. Belmonte. Carbonitruration des aciers faiblement alliés: rôles du carbone et de l'azote sur les réponses mécaniques et métallurgiques.}

\ecvitem[10pt]{}{7$^{th}$ International Conference on Inovations in Thin Film Processing and Characterization, Nancy, France, 16th to 20th November 2015. Oral presentation. W. Dal'Maz Silva, J. Dulcy, G. Michel, P. Lamesle, T. Belmonte. The roles of carbon and nitrogen on metallurgical response of low alloy steels to carbonitriding.}

\ecvitem[10pt]{}{42$^e$ Congrès du Traitement Thermique et de l'Ingénierie des Surfaces. Saint-Etienne, France, 2nd to 4th June 2015. Oral presentation. W. Dal'Maz Silva, J. Dulcy, G. Michel, P. Lamesle, T. Belmonte. Traitements thermochimiques des alliages 16NiCrMo13 et 23MnCrMo5: le rôle du carbone et de l'azote sur les réponses métallurgiques à la carbonitruration.}

\ecvitem[10pt]{}{22$^{nd}$ International Federation for Heat Treatment and Surface Engineering Congress, Mestre, Italy, 20th to 22nd May 2015. Oral presentation. W. Dal'Maz Silva, J. Dulcy, G. Michel, P. Lamesle, T. Belmonte. Thermochemical treatments of alloys 16NiCrMo13 and 23MnCrMo5: the roles of carbon and nitrogen on metallurgical response to carbonitriding.}%

\endinput%